Case Study Reasoning about BYOD Policies in the Healthcare Sector

### 2016-08-01 paper.tex
updates done in edinburgh

@@

Armando~\etal~created a BYODroid~\cite{armando_bring_2013}; \ac{BYOD} framework to enforce \ac{BYOD} policies by extending Featherweight Java~\cite{igarashi_featherweight_2001} with a type system that can describe how Android apps interact.  Whilst this work gives a framework for enforcing policies on Android, it doesn't help policy authors decide what the policies should be to begin with.

>>>>

\subsection{Delegation}
\textit{About a page to be merged from the other machine you forgot to push. }

@@

Armando~\etal~created a BYODroid~\cite{armando_bring_2013}; \ac{BYOD} framework
to enforce \ac{BYOD} policies by extending Featherweight
Java~\cite{igarashi_featherweight_2001} with a type system that can describe how
Android apps interact. Whilst this work gives a framework for enforcing policies
on Android, it doesn't help policy authors decide what the policies should be to
begin with. They went on to show how BYODroid could be used to enforce a {NATO}
Communications and Information Agency policy~\cite{armando_developing_2016}.
Armando~\etal also proposed creating curated app stores based on corporate BYOD
policies~\cite{armando_enabling_2014}. To do this they analysed a BYOD policy
taken from the US Government BYOD Security
Guidelines~\cite{digital_services_advisory_group_and_federal_chief_information_officers_council_bring_????}~and
translated it into rules in the CONspec~\cite{aktug_conspec_2008} language which
allows a low-level description of app behavior based on Java code. They then
used these rules to filter apps for their store from a selection of 860 apps
taken from the \emph{top selling free} section of the Google Play store.

Martinelli~\etal~applied the UCON security model to describe \ac{BYOD} policies
for Android~\cite{martinelli_enhancing_2016}. Using this model they created an
enforcement framework that could alter the permissions granted to Android apps
at run time. This framework requires a rooted device for most Android versions,
however, they do claim it should work without modification on the latest
version. Again like the work of Armando~\etal, this gives a framework for
enforcement but without consideration of what the policies should be enforcing.

Hong~\etal~focussedon the network aspects of a \ac{BYOD} policy with their
PBS-Droid tool~\cite{sungmin_hong_towards_2016}.  PBS-Droid allowed BYOD policy
authors the ability to sandbox individual apps into their own software-defined
networks giving finer control over how individual apps interact with a companies
networks and allowing for dynamic policy enforcement and network configuration.

For more general mobile policies, there has been extensive work in both
modeling and enforcing various policies.  Sadeh~\etal~surveyed users to find
their privacy preferences and found four different types of user each with
different privacy policies~\cite{sadeh_understanding_2009}.  Various tools have
been proposed that can enforce app behavior policies.  Aurasium works by
repackaging apps to use modified APIs~\cite{xu_aurasium:_2012}.  These APIs can
enforce policies to protect a user's personal information or prevent sending
premium rate text messages.  Another tool, CRePE~\cite{conti_crepe:_2010}
modifies Android to provide a framework that can enforce policies based
on the contextual information, such as the device's location or battery level.
The SEAR tool takes a different approach and actively scans apps for
vulnerabilities over collections of apps.  It then outputs security policies
that users might want to enforce in order to prevent attacks from occurring in
the first place~\cite{bagheri_practical_2016}.
